\documentclass{article}
\usepackage{amsmath}
\usepackage{cjhebrew}
\usepackage[LGR,T1]{fontenc}
\newcommand{\donaldiv}{\textgreek{Ντόναλντ Δ }}
\newcommand{\textgreek}[1]{\begingroup\fontencoding{LGR}\selectfont#1\endgroup}\newcounter{example}[section]
\newenvironment{example}[1][]{\refstepcounter{example}\par\medskip
   \noindent \textbf{Example~\theexample. #1} \rmfamily}{\medskip}

\title{Gauss-Bonet Theorem}
\author{\textgreek{Για Ντόναλντ Ιορδανιδου Δ}}
\begin{document}
\maketitle

The Gauss-Bonnet Theorem is a formula linking the curvature of a surface to its topology.
\begin{equation}
    \int_M K\,dA + \int_{\partial M} k_g \,ds = 2\pi\chi(M)
\end{equation}

\section{Descriptions}
There are a few functions within the theorem that would require descriptions unto themselves.
In this section, they will be explained.

\subsection{Curvature}
Curvature is often represented by the greek letter $\kappa$.
There are multiple formulae that would be equivalent to $\kappa$.
\begin{gather}
    \kappa  =   \left|\left|\frac{d\vec{T}}{ds}\right|\right|
        =   \frac{\left|\left|\vec{T}'(t)\right|\right|}{\left|\left|\vec{r}\ '(t)\right|\right|}
        =   \frac{\left|\left|\vec{r}\ '(t) \times \vec{r}\ ''(t)\right|\right|}{\left|\left|\vec{r}\ '(t)\right|\right|^3}
\end{gather}

\begin{example}
    The case of a sphere.\\
    A sphere has an equation for it. 
    \[
        x^2 + y^2 + z^2 = r^2
    \]

    This can be rewritten to form a formula of $r$.
    \[
        r(t) = \sqrt{x(t)^2 + y(t)^2 + z(t)^2}
    \]

    We can rewrite this in polar coordinates.
    \begin{align*}
        x(t)    &=  r*\sin(\theta)\cos(\phi)\\
        y(t)    &=  r*\sin(\theta)\sin(\phi)\\
        z(t)    &=  r*\cos(\theta)
    \end{align*}
    % \begin{align*}
    %     \kappa
    % \end{align*}
\end{example}

\subsection{Euler's Characteristic}
It wouldn't be math if Euler wasn't hiding in there somewhere (\<'wyy>). 
Euler's characteristic, represented as a function with $\chi(M)$, is a function that tracks the number of objects of each dimension. 
A \donaldiv description of this would be, for $k_i$ being the number of $i-dimensional$ components of the overall object:
\begin{equation}
    \chi(M) = \overunderset{\infty}{i = 0}{\Sigma} k_i (-1)^i 
\end{equation}

\begin{example}\\
    $\chi(line) = 2 - 1 = 1$\\
    $\chi(quadrilateral) = 4 - 4 + 1 = 1$\\
    $\chi(5\ point\ star) = 10 - 10 + 2 = 2$\\
    $\chi(dodecahedron) = 20 - 30 + 12 = 2$\\
    $\chi(tesseract) = 16 - 32 + 18 - 2 = 0$
\end{example}

\section{Related Theorems}
\subsection{Theoreme de Descartes}
René n'était pas un philosopheur. 
Il était un mathématicien qui a appliqué les règles des preuves de mathématiques à des règles qu'il s'est inventé.
``Je pense donc je suis'' n'était pas une conclusion, c'était un postulat q'il s'est donné.
Qui autre d'un mathématicien pourrait nous donner le plan cartésien. 

\section{}

% Bibliography
% https://e.math.cornell.edu/people/belk/differentialgeometry/Outline\%20-\%20The\%20Gauss\%20Map.pdf
% https://en.wikipedia.org/wiki/Descartes\%27_theorem
% https://www2.math.upenn.edu/~shiydong/Math501X-7-GaussBonnet.pdf
% https://www.math.stonybrook.edu/~tony/whatsnew/column/descartes-0899/descartes1.html
% https://math.stackexchange.com/questions/3920357/why-isnt-the-euler-characteristic-equal-to-2-for-this-polyhedron

\end{document}